A Machine-checked Proof of the Average-case Complexity of Quicksort in Coq

### 2008-08-29 paper/paper.tex
optional arguments to \cite
darcs-hash:20080829130912-d98fc-6e36b8a61a0f1dc2eb78008f778c1ffea06c5cea.gz

Proofs of Quicksort's $O(n \log n)$ average-case complexity are included in many textbooks on computational complexity \cite{introtoalgos} \todo{more}. This paper documents what the authors believe to be the first fully formal machine-checked version of such a proof, developed using the Coq proof assistant \cite{coq}.

>>>>

Proofs of Quicksort's $O(n \log n)$ average-case complexity are included in many textbooks on computational complexity \cite[for example, which we followed in this course of this research]{introtoalgos}. %%% \todo{more}. 
This paper documents what the authors believe to be the first fully formal machine-checked version of such a proof, developed using the Coq proof assistant \cite{coq}.
